\section{Introduction}

In this project we will design and implement a mobile device app to help track and manage personal data the solution must also secure, filter or bring added value to that data. The project will be entered into the Atos IT Challenge 2016 \emph{``The Right to be Forgotten: manage your online persona''}.

\subsection{The Client}

Atos S.E.~(ATO) is a France-based company that provides IT services~\parencite{web:reuters}. The company provides an assortment of services, including: bespoke enterprise software, e-payment services, business integration solutions and cloud services. In addition, the company serves clients in various industries, including: energy and utilities, financial services, manufacturing, retail, public sector, healthcare and transport. Over time, Atos has developed strategic alliances with Cisco, Dell, EMC, Hitachi, Microsoft, Oracle, Samsung, SAP, Siemens and VMWare; and strategic business partnerships with HP and IBM~\parencite{web:bloomberg}. This has allowed them to significantly leverage their service offerings and develop the credibility required to attract new trade. For example, the company was recently awarded a \pounds 6m contract to run Transport for London's service desk, a move that will see them responsible for logging, tracking and managing requests such as e-mail configuration, printing and remote access for 25\,000 users across multiple locations~\parencite{web:jee}.

\subsection{The Project}

The group has been tasked with the job of creating a solution to track and identify one’s online personal data on behalf of Atos. The solution must be capable of securing, filtering or bringing added value to the data. Consequently, the group must start thinking about actions, functionalities or objectives that might be useful in the solution to protect personal data, for example: automatic de-subscription, notifications, deletion, or ensuring results do not appear in search engine top hits.

\subsection{The Team}

The following section outlines the expected roles and responsibilities for each individual involved in this project. However, due to the dynamic nature of the project, roles may be re-assigned to one or more individuals throughout the duration of the project. As a result, individuals may need to play a different role than that which was initially outlined. This approach to team development correlates to~\textcite{book:xteams} ideas on adaptive team structure within organisations:

\subsubsection{Jeansy Molanza -- Project Management/Business Analyst}

As Project Manager, responsible for the successful initiation, planning, execution, monitoring, controlling and closure of the project. As Business Analyst, responsible for the design of solutions that will deliver value to stakeholders -- acting as an agent of change whenever necessary.

\subsubsection{Gary Bennett -- Front End Development/Business Analyst}

As Front End Developer, responsible for implementing interactive elements, translating UI/UX wireframes to actual code that will produce the solution's interface that the end user engages with. As Business Analyst, responsible for the bridging the gap between technical and project requirements.

\subsubsection{Jifei Wei/Rawand Hawiz -- Back End Development}

As Back End Developer, responsible for implementing server-side application logic; creating the application's API to facilitate database interaction and intelligent agents tasked with performing a service on a regular schedule. In addition, will be in charge of writing unit tests and source control.
